\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-15 report/paper.tex
alhpa factors

    \begin{equation} \label{eq:nsDensity}
        \frac{D\rho}{Dt} = 0 \Leftrightarrow \bigtriangledown \cdot \textbf{v} = 0 
    \end{equation}

    \begin{equation} \label{eq:nsVelocity}
        \frac{D\textbf{v}}{Dt} = -\frac{1}{\rho} \bigtriangledown p + v \bigtriangledown ^2 \textbf{v} + \frac{\textbf{f}}{\rho}
    \end{equation}

    In the equations $\frac{D\rho}{Dt}$ and $\frac{D\textbf{v}}{Dt}$ denotes the derivate of the density $\rho$ and the velocity $\textbf{v}$ respectively. The pressure, kinematic viscosity and body forces are denoted by $p,v$ and $\textbf{f}$ respectively. The second part of Equation~\ref{eq:nsDensity} $\bigtriangledown \cdot \textbf{v} = 0$ induce that the velocity field is free from divergence. From the continuity equation $\frac{D\rho}{Dt} = -\rho \bigtriangledown \cdot \textbf{v}$ and the divergence-free condition it follows that the partial derivate of the density with respect to the time is zero, which implies the equivalence of the equations in Equation~\ref{eq:nsDensity}. From this is follows that the density, in theory, must stay constant over time which is the implication of an incompressible fluid. In practice the divergence-free condition is not sufficient to guarantee incompressibility in simulations. The numerical time integrations will contain numerical errors which will cause density deviations due to the volume compressions. To avoid this a second condition $\rho - \rho_0 = 0$ called \textit{constant density condition} must be fullfilled~\cite{bender}. Bridson~\cite{bridson} uses splitting on Equation~\ref{eq:nsVelocity} which induce $\frac{D\textbf{v}}{Dt} = -\frac{1}{\rho} \bigtriangledown p$ which will be used further on in the simulation. Section~\ref{divergenceSolver} and~\ref{densitySolver} give a deeper description of the solvers used in the project.

@@

@@

    \begin{equation} \label{eq:predDensity}
        \resizebox{0.88\linewidth}{!}{$
        \begin{matrix}
        \rho_i^* = \rho_i + \Delta t \frac{D\rho_i}{Dt} \\ 
        \\
        \Leftrightarrow \\ 
        \\
        \rho_i^* = \rho_i + \Delta t + \sum_j m_j 
        (\textbf{v}_i^* - \textbf{v}_j^*) \nabla W_{ij}
        \end{matrix}
        $}
    \end{equation}

@@

    \begin{equation} \label{eq:pressure2}
        \vect{F_{j\leftarrow i}^p} = -\frac{m_i}{\rho_i} \kappa_i^v m_j \nabla W_{ij}
    \end{equation}

@@

    \begin{equation} \label{eq:pressureTotal}
        \resizebox{0.88\linewidth}{!}{$
        \begin{matrix}
            \vect{F_{i,total}^p} = \vect{F_i^p} + \sum_j \vect{F_{i\leftarrow j}^p} \\
            \\
            \Leftrightarrow \\ 
            \\
            \vect{F_{i,total}^p} = -m_i \sum_j m_j (\frac{\kappa_i^v}{\rho_i} + \frac{\kappa_j^v}{\rho_i}) \nabla \vect{W_{ij}}
        \end{matrix}
        $}
    \end{equation}

@@

    \begin{equation} \label{dvdt}
        \frac{dv}{dt} = \sum_j m_j (\frac{\kappa_i^v}{\rho_i} + \frac{\kappa_j^v}{\rho_i}) \nabla \vect{W_{ij}}
    \end{equation}

@@

    \begin{equation} \label{eq:velocity}
        \vect{v_i^*}(t) = \vect{v_i^*}(t) - \Delta t \sum_j m_j (\frac{\kappa_i^v}{\rho_i} + \frac{\kappa_j^v}{\rho_i}) \nabla \vect{W_{ij}}
    \end{equation}

@@

    \begin{equation} \label{eq:dpdt}
        \frac{D\rho_i}{Dt} = \sum_j m_j (\vect{v_i} - \vect{v_j})\nabla \vect{W_{ij}}
    \end{equation}

    \begin{equation}\label{eq:kappaDivergence}
        \kappa_i^v = \frac{D\rho}{Dt} \cdot \frac{\rho_i}{\Delta t \cdot \alpha_i}
    \end{equation}

>>>>

    \begin{equation} \label{eq:nsDensity}
        \frac{D\rho}{Dt} = 0 \Leftrightarrow \nabla \cdot \textbf{v} = 0 
    \end{equation}

    \begin{equation} \label{eq:nsVelocity}
        \frac{D\textbf{v}}{Dt} = -\frac{1}{\rho} \nabla p + v \nabla ^2 \textbf{v} + \frac{\textbf{f}}{\rho}
    \end{equation}

    In the equations $\frac{D\rho}{Dt}$ and $\frac{D\textbf{v}}{Dt}$ denotes the derivate of the density $\rho$ and the velocity $\textbf{v}$ respectively. The pressure, kinematic viscosity and body forces are denoted by $p,v$ and $\textbf{f}$ respectively. The second part of Equation~\ref{eq:nsDensity} $\nabla \cdot \textbf{v} = 0$ induce that the velocity field is free from divergence. From the continuity equation $\frac{D\rho}{Dt} = -\rho \nabla \cdot \textbf{v}$ and the divergence-free condition it follows that the partial derivate of the density with respect to the time is zero, which implies the equivalence of the equations in Equation~\ref{eq:nsDensity}. From this is follows that the density, in theory, must stay constant over time which is the implication of an incompressible fluid. In practice the divergence-free condition is not sufficient to guarantee incompressibility in simulations. The numerical time integrations will contain numerical errors which will cause density deviations due to the volume compressions. To avoid this a second condition $\rho - \rho_0 = 0$ called \textit{constant density condition} must be fullfilled~\cite{bender}. Section~\ref{divergenceSolver} and~\ref{densitySolver} give a deeper description of the solvers used in the project.

@@

    Both the density solver and the divergence solver uses a stiffness parameter $\kappa_i^v$ presented by Bender et. al.~\cite{bender}, Equation~\ref{eq:kappa}.

    \begin{equation}\label{eq:kappa}
        \kappa_i^v = \frac{1}{\Delta t} \frac{D\rho_i}{Dt} \cdot \alpha_i
    \end{equation}

    In the equation $\Delta t$ denotes a small time step and $\alpha_i$ is a precomputed factor to decrease the computations while performing the solvers. Bender et. al.~\cite{bender} defines $\alpha_i$ as

    \begin{equation}\label{eq:alpha}
        \alpha_i = \frac{\rho_i}{\left | \sum_j m_j \nabla \vect{W}_{ij}  \right |^2 + \sum_j \left | m_j \nabla \vect{W}_{ij} \right |^2}
    \end{equation}

    where $\vect{W}_{ij}$ corresponds to the kernel gradient.

@@

    \begin{equation} \label{eq:predDensity}
        \resizebox{0.88\linewidth}{!}{$
        \begin{matrix}
        \rho_i^* = \rho_i + \Delta t \frac{D\rho_i}{Dt} \\ 
        \\
        \Leftrightarrow \\ 
        \\
        \rho_i^* = \rho_i + \Delta t + \sum_j m_j 
        (\textbf{v}_i^* - \textbf{v}_j^*) \nabla \vect{W}_{ij}
        \end{matrix}
        $}
    \end{equation}

@@

    \begin{equation} \label{eq:pressure2}
        \vect{F_{j\leftarrow i}^p} = -\frac{m_i}{\rho_i} \kappa_i^v m_j \nabla \vect{W}_{ij}
    \end{equation}

@@

    \begin{equation} \label{eq:pressureTotal}
        \resizebox{0.88\linewidth}{!}{$
        \begin{matrix}
            \vect{F_{i,total}^p} = \vect{F_i^p} + \sum_j \vect{F_{i\leftarrow j}^p} \\
            \\
            \Leftrightarrow \\ 
            \\
            \vect{F_{i,total}^p} = -m_i \sum_j m_j (\frac{\kappa_i^v}{\rho_i} + \frac{\kappa_j^v}{\rho_i}) \nabla \vect{W}_{ij}
        \end{matrix}
        $}
    \end{equation}

@@

    \begin{equation} \label{dvdt}
        \frac{dv}{dt} = \sum_j m_j (\frac{\kappa_i^v}{\rho_i} + \frac{\kappa_j^v}{\rho_i}) \nabla \vect{W}_{ij}
    \end{equation}

@@

    \begin{equation} \label{eq:velocity}
        \vect{v_i^*}(t) = \vect{v_i^*}(t) - \Delta t \sum_j m_j (\frac{\kappa_i^v}{\rho_i} + \frac{\kappa_j^v}{\rho_i}) \nabla \vect{W}_{ij}
    \end{equation}

@@

    \begin{equation} \label{eq:dpdt}
        \frac{D\rho_i}{Dt} = \sum_j m_j (\vect{v_i} - \vect{v_j})\nabla \vect{W}_{ij}
    \end{equation}

    \begin{equation}\label{eq:kappaDivergence}
        \kappa_i^v = \frac{1}{\Delta t} \frac{D\rho_i}{Dt} \cdot \alpha_i
    \end{equation}
